% extracurriculars.tex

\headedsection{\href{http://liquidrocketry.com/}{Liquid Rocketry Lab}}
{\textsc{Raleigh, NC}}
{\headedsubsection{Chief Business Officer}
	{Aug \apo18-- May \apo20}
	{%
		\bodytext{%
			Founded and developed NC's first liquid propulsion laboratory developing a space bound rocket (Karman Line, 100\textsmaller{km})
			\begin{tightemize}
				\item Recruited a talented, diverse core team of 50 students.
				\item Managed a team of 15 students to raise \$250,000. Brokered partnerships with companies such as RedBull and Jacobs.
				\item Managed legal matters including nonprofit registration, tax exempt status and insurance procurement.
			\end{tightemize}
		}
	}
}

\headedsection{\href{http://ewh.ieee.org/sb/nc/ncsu/}{NC State IEEE Chapter}}
{\textsc{Raleigh, NC}}
{\headedsubsection{President, Chair}
	{Aug \apo17--May \apo20}
	{%
		\bodytext{%
			Responsible for the largest professional society at NC State.
			\begin{tightemize}
				\item Established a \$400 scholarship for students in the ECE department
				\item Increased student membership by 20\% (to 400\textsmaller{+} members) by conducting technical talks of interest to members.
				\item Coordinated the yearly student delegation to the South East Regional conference where the team has won 5\textsmaller{+} awards.
				\item Organized the NC State IEEE Extreme Hackathon with significant student participation. (2017, 2018, 2019)
			\end{tightemize}
		}
	}
}

\headedsection{\href{https://ncstatefirstalumni.com/}
	{NC State FIRST Alumni Association}}
{\textsc{Raleigh, NC}}
{\headedsubsection{President}
	{Aug \apo18--May \apo19}
	{%
		\bodytext{%
			Founded and grew North Carolina's first collegiate alumni program for high school robotics participants.
			\begin{tightemize}
				\item Grew the organization to over 70 members in the first year.
				\item Organized a special event with FIRST's founder, Dean Kamen, at NC State.
				\item Empowered students to volunteer for over 1,000 hours across local FIRST robotics events in dire need of help through club funds.
			\end{tightemize}
		}
	}
}

\headedsection{%
	\href{https://www.tbp.org/off/DisplayChapterInfo.cfm?ID=129}{Tau Beta Pi NC Alpha Chapter}
}
{\textsc{Raleigh, NC}}
{%
	\headedsubsection{Vice President}
	{Aug \apo18--May \apo19}
	{%
		\bodytext{%
			Responsible for managing the organization's day-to-day operations of the largest honors society at NC State.
			\begin{tightemize}
				\item Assisted in the organization of professional development and volunteering events for student induction requirements.
				\item Inducted a class of the top 30 students in the engineering department into the prestigious society.
			\end{tightemize}
		}
	}
}

\headedsection{\href{https://team900.org/}{Robotics at NCSSM}}
{\textsc{Durham, NC}}
{%
	\headedsubsection{Team Captain}
	{Aug \apo15--May \apo17}
	{%
		\bodytext{%
			Responsible for delivering strong competition results for one North Carolina's oldest robotics teams.
			\begin{tightemize}
				\item Managed a team of 50 students to fabricate a 120 lb.\ robot in the span of 6 weeks to compete in a yearly challenge.
				\item Successfully spearheaded significant technical advancements in robot perception and control using deep learning and ROS, respectively.
				\item Led the team to a world championship quarterfinal berth and, later, open sourced our winning code.
			\end{tightemize}
		}
	}
}
% I led the team to the World Championship and spearheaded the adoption of cutting edge technologies to empower robot automation. As Computer Vision Lead, I worked specifically on developing computer vision and advanced robot perception solutions for competition challenges. I also developed curriculum to teach new members the skills they would need to succeed on the computer vision sub-team. As Project Manager, I integrated the multiple sub-teams, kept track of project status, presented on behalf of the team, and procured funding sources.
% ROS for FRC whitepaper (in publications section)
% FRC900 Repo (I have a fork in my repos)

\headedsection{%
	\href{https://web.archive.org/web/20181221034926/https://www.ncssm.edu/residential-program/academics/sustainability}{Sustainability at NCSSM}
}
{\textsc{Durham, NC}}
{%
	\headedsubsection{Sustainability Project Leader}
	{Aug \apo16--May \apo17}
	{%
		\bodytext{%
			Managed the implementation of the strategic sustainability vision of the school.
			\begin{tightemize}
				\item Created and performed Energy Star portfolio analysis for the school and made recommendations to reduce the carbon footprint.
				\item Converted the cafeteria to a zero waste zone through a partnership with local composting organization, CompostNow.
			\end{tightemize}
		}
	}
}
% Sustainability is a core part of NCSSM's strategic plan and student-led initiatives are a large part of progressing this vision. As a Sustainability Project Leader, I collected data metrics and compiled a portfolio of the school's progress towards overall sustainability. As a team, we implemented a commercial composting program in the residential cafeteria which brought the space closer to becoming a zero-waste zone.

\headedsection{%
	\href{https://beaverworks.ll.mit.edu/CMS/bw/}{MIT Lincoln Laboratory}
}
{\textsc{Boston, MA}}
{%
	\headedsubsection{Beaver Works Summer Institute Member}
	{Aug \apo16--May \apo17}
	{%
		\bodytext{%
			Developed and programmed a miniature autonomous car.
			\begin{tightemize}
				\item One of 46 students selected to develop a miniature autonomous cars covered under a full scholarship.
				\item Developed skills in ROS, Sensor fusion, computer vision, path planning under guidance from faculty from MIT and NASA JPL.\@
			\end{tightemize}
		}
	}
}
