% projects.tex

\newcommand{\eclinic}[1]{\href{https://entrepreneurship.ncsu.edu/spaces/entrepreneurship-clinic/}{#1}}

\inlineheadsection{\href{https://github.com/georgianpartners/foreshadow}{Foreshadow:}}
{%
	An automatic machine learning (AutoML), pipeline package built on top of \texttt{sklearn} and \texttt{pandas} to intuitively construct and tune machine learning models in Python.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/georgianpartners/automl_benchmark}{AutoML Benchmarking:}}
{%
	A command line utility to scalably validate the performance of open source AutoML solutions.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/loanchain}{Loanchain:}}
{%
	A novel smart contact generator utilizing the Ethereum blockchain to broker transparent loan agreements. Used an oracle voting architecture to resolve loan interest rates.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/EmbeddedSysCar}{Embedded Systems Car:}}
{%
	An embedded systems car from the ground up using TI's MSP 430 development board. Features included, a scrolling LCD menu and an autonomous mode using PID control.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/CreditSuisseProject}{Credit Suisse NLP Model:}}
{%
	A machine learning model that constructs a user profile for developer on boarding steps based on job descriptions. Developed this as a part of \eclinic{NC State Entrepreneurship Clinic} at HQ Raleigh.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/Entrust}{Entrust (GoFundMe for Loans):}}
{%
	A business case / hackathon project to build a peer-to-peer loan system with a full design concept alongside a machine learning model to automatically set loan rates based on federal interest rates. Recognized as the university winner.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/music_dev}{YCombinator Hackathon (2018): Duolingo for Music}}
{%
	Invited to Mountain View to compete in a 24 hour product hackathon. Develop the DuoLingo for instruments with an MVP that used advanced signal processing to provide user feedback and instrument play style.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/NBAResearch}{NBAHackathon:}}
{%
	A player lineup optimization model using LSTM based deep neural network architecture that efficiently parsed aggregated play by play data.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/ProjectSocrates}{VideoVote:}}
{%
	A Twitch bot that builds an ephemeral MTV for YouTube where the chat could vote on the top video they wanted to see.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/2017VisionCode}{ROS for FIRST Robotics:}}
{%
	The first implementation of the Robot Operating System (ROS) robot sensor information processing protocol at the high school level of robotics.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/LanderControls}{High Power Rocketry Payload:}}
{%
	A sensor bay payload deployed from a high power rocket launched to 5000 feet. Interested features include a spring loaded camera and embedded operating system that uses ROS to transmit telemetry back to a ground station.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/simplecalc}{Simplecalc (Python DevOps):}}
{%
	An example repository that accompanies a Medium blog on Python DevOps best practices.
}

\vspace{0.5em}

\inlineheadsection{\href{https://github.com/adithyabsk/NCSUIEEEWebsite}{NC State IEEE Website:}}
{%
	The open source website that powers the NC State IEEE Student Branch.
}

\vspace{0.5em}

\inlineheadsection{\href{https://seamlessfits.com}{YCombinator Hackathon (2019): SeamlessFits}}
{%
	A new look into social fashion. A mobile platform to explore and buy clothes that are trending in just a few clicks.
}